\documentclass[a4paper]{style/dnd4e}
\begin{document}
\pagestyle{empty}

\newtoggle{DM}
\toggletrue{DM}
%\togglefalse{DM}




\section*{The New Gods}

\subsection*{The Northern Gods}
The barbarian gods, worshipped by men in Cheruskia and Hyperboria and some of Hibernia.


\subsubsection*{Gromm} 
\sigil{Lightning Bolt}
\words{Ord kan ikke redde deg (Words cannot save you)}
\colours{Black}
\alignment{Neutral}

Gromm is a grim and unforgiving god, ever watching 
from atop his mountain in dark clouds and obscuring mists, ready to 
pass a disapproving judgment on any and all. However, he is also 
said to value courage and tenacity in mortals.
  
It is best to avoid doing anything that would draw Gromm's attention,
as the god brings down only trouble and doom. As a result, he is 
not so much worshipped as invoked in curses and expletives, or when 
trying to gather one's courage. This does not however imply that he 
ever does anything, good or bad, to mortals; it is said that his 
sole gift to men is to bestow them at birth with the courage to 
survive, persevere, and vanquish adversity.


\subsubsection*{Lir}
\sigil{Sailfish}
\words{Jeg frykter ikke (I fear not)}
\colours{Light Grey}
\alignment{Neutral Good}

Barbarian father god of the sea, sailors, and good fortune. 


\subsubsection*{Balinor}
\sigil{Wolf Rampant}
\words{Død og kamp (death and battle)}
\colours{Black and Red Stripes}
\alignment{Neutral}
Wolf-headed god of the hunt and battle rage. 


\subsubsection*{Beltain}
\sigil{Ox Head}
\words{Hva du planter du wil innhøsting (What you plant you will harvest)}
\colours{Flax}
\alignment{Neutral Good}
Goddess of the Harvest and of the Hearth.  Appears as a blonde haired beauty.  


\subsubsection*{Boldrei}
\sigil{Sparrow}
\words{I alle ting det er magi (In all things there is magic)}
\colours{Maroon}
\alignment{Neutral}
God of Magic, the Winds and the Seasons.    

  
\subsubsection*{Cthugha}
\sigil{Flame}
\words{Branner må mates (Fires must be fed)}
\colours{Yellow}
\alignment{Lawful Evil}
The Living Flame, The Burning One, Appears as a living conflagration.  


\subsubsection*{Onator}
\sigil{Sheaf of Wheat}
\words{Hva ble spredt samler.  Hva ble samlet blåser bort (What was scattered
gathers. What was gathered blows away)}
\colours{Aureolin}
\alignment{Lawful Neutral}
Goddess of the Harvests, Marriage and Fertility.    
  

\subsubsection*{Shuma-CGorath}
\sigil{Eye with tentacles}
\words{Som sover, men skal vekke (Who Sleeps, but Shall Awake)}
\colours{}
\alignment{Chaotic Evil}
Lord of Chaos, Master of the Old Ones, Ruler of a hundred dimensions. 


\subsubsection*{Yhoundeh}
\sigil{Elk Skull}
\words{Alle mennesker er dødelige (All men are mortal})
\colours{White}
\alignment{Neutral Evil}
The Elk goddess.  God of Death, the Ice Maiden.  



\subsection*{The Gods of Civilised Men}
Gods worshipped in Aquilonia, Brythynia, Averoigne and to a lesser 
extent the Border Principalities, Thule, Hybernia, Cormyr, Hyperboria and 
Cheruskia.

\subsubsection*{Blind Aureon}
\sigil{Sword with a Halo}
\words{Ab aeterno (from the beginning of time)}
\colours{Gold}
\alignment{Good}
The one father.  Aureon is the ruler of the gods, he dispenses justice.
Noted for hsi wisdom.  Priests blindfold themselves and he guides them.
  

\subsubsection*{Barrizhan}
\sigil{Golden Chalice}
\words{Ab imo pectore (From the bottom of the chest. (from the heart))}
\colours{Platinum}
\alignment{Neutral}
God of money lenders, luck, good fortune, gamblers and thieves.  
  

\subsubsection*{Oranah} 
\sigil{A candle and a dagger}
\words{Puris omnia pura (To the pure all things are pure)}
\colours{White}
\alignment{Good}
The protector.  The wife of Aureon, Oranah is typically portrayed as a common woman. 
  

\subsubsection*{Mitra}
\sigil{Blazing Sun}
\words{Libertas Perfundet Omnia Luce (Freedom will flood all things with light)}
\colours{Red}
\alignment{Good}
The sun god.  God of War, Sacrifice and of Victoty.


\subsubsection*{Chthon}
\sigil{Black Candle}
\words{Pulvis et umbra sumus (we are dust and shadow)}
\colours{Black}
\alignment{Chaotic Evil}
Lord of Decay.    
Illegal to follow this deity.


\subsubsection*{Morr}
\sigil{Skull with a Jesters Cap}
\words{Cineri gloria sera est (Glory paid to ashes comes too late)}
\colours{Ivory}
\alignment{Neutral}
God of Death    


\subsubsection*{The Black Goat}   
\sigil{Black Goats Head}
\words{Summum malum (the supreme evil)}
\colours{Brown}
\alignment{Lawful Evil}  
The Black Goat of the Woods with a Thousand Young.  Illegal to follow this deity.
Worshipped by Skaven and members of the Black Cathedral.

\subsubsection*{Tyaa}   
\sigil{Birds Claw}
\words{Cum incipit esse cum columba candida, cor autem ejus manet corvorum plumis suis denigrata.  (When a dove meets with crows its feathers remain white but its heart grows black.)}
\colours{Yellow}
\alignment{Neutral Evil}  
Goddess of birds and ill fortune.


\subsubsection*{Omm}
\sigil{Spider}
\words{Verbis arma (Words are our weapons}
\colours{Red}
\alignment{Chaotic Evil}
Illegal to follow this deity.
The Spider God, deception, assassination, mendacity and revenge.


\subsubsection*{Aran}
\sigil{Stag}
\words{Respice in me, et turbo coram tempestate. (Look for me in the whirlwind or the storm)}
\colours{Silver}
\alignment{Chaotic Neutral}
God of Nature and the Hunt. 

\subsubsection*{Caiphon}
\sigil{Flail}
\words{Post tenebras lux (after darkness, light).}
\colours{White}
\alignment{Lawful Neutral}
God of Purity.  Followers practice eugenics and seek to purify the world through genocide and 
self-flagellation.  There are, famously, events known as the 1703 smitings of Caiphon where 
Caiphon struck down the unclean.  The predominant prophet of Caiphon was Egbert of Aginor, who marched from Aginor through Averoigne and gathered an army unto him which he used to crush the Orcish horde .


\subsubsection*{Weland the Smith}
\sigil{Anvil}
\words{Clypeus homines (The shield of mankind)}
\colours{Bronze}
\alignment{Neutral Good}
God of Armourers and fighters.  Protector of men.


\subsubsection*{Zehir}
\sigil{Snake}
\words{Bibere venenum in auro (Drink poison from a cup of gold)}
\colours{Green}
\alignment{Evil}  
The Promiser. God of Snakes, greed and the granting of wishes.  Illegal to follow this deity.



\subsection*{The Gods of the Elves}

Elves practice a form of animism.  They believe that trees, rivers, and mountains 
possess a spiritual essence.  These spirits form a hierarchy with Mab as their head.
A few other powerful lords of the Elven pantheon are also listed below.

\subsubsection*{Summanus}
\sigil{Solar Eclipse}
\words{Foinse solaibs (The source of the light)}
\colours{Yellow}
\alignment{Chaotic Neutral}
God of change.

\subsubsection*{Silvannus} 
\sigil{Pine Tree}
\words{Máthair de mo (Mother of mine)}
\colours{Green}
\alignment{Neutral}
God of the Forests

\subsubsection*{Oberon}
\sigil{Crown}
\words{Thar go léir (Over all)}
\colours{Green}
\alignment{Neutral}
King of the Gods (note the title King is honorary and denotes the consort of the Queen).

\subsubsection*{Mab}  
\sigil{Raven}
\words{Banríon na Fey (Queen of the Fey)}
\colours{Blue}
\alignment{Neutral Evil}
Queen of the Fairies.

\subsubsection*{Oceannus}  
\sigil{Porpoise}
\words{Fuaim agus fury (Sound and Fury)}
\colours{Blue}
\alignment{Lawful Neutral}
God of the Seas and the Rivers and their inhabitants.
  
\subsubsection*{Lolth}
\sigil{Spider}
\words{Faireoir san oíche (watcher in the night)}
\colours{Black}
\alignment{Lawful Evil}
Goddess of suffering, pain, death, disease, dark deeds and spiders.

\subsubsection*{Khaine}
\sigil{Blood Drenched Hand}
\words{Lig ann a doirteadh fola (Let there be bloodshed)}
\colours{Black}
\alignment{Lawful Evil}
Elven god of War.



\subsection*{The Gods of the Dwarves}

\subsubsection*{Grombindal}   
\sigil{Hammer}
\words{Festhalten (Hold Fast)}
\colours{Gold}
\alignment{Neutral Good}
  
King of the Dwarven gods.  Some (human) 
scholars claim that Grombindal merely an aspect of the barbarian 
god Grom, the dwarves hotly dispute this claiming that in fact 
Grom is an aspect of Gombrindal.  In any case, Grombindal is the 
king of the dwarven gods.  


\subsubsection*{Trowkee}   
\sigil{Five Bar Gate}
\words{Es soll Rache sein (There shall be retribution).}
\colours{Silver}
\alignment{Neutral}
Dwarven God of Thieves, Tricksters, and Shysters (there is an on ongoing joke in Dwarven society
that Trowkees followers also includes Accountants, Lawyers and Administrators).
Trowkee stole the Arkstone and some say that this led to the fall of the original Dwarven
city and the exodus of the Dwarves from the East.  There are many stories depicting
Trowkee tricking people to get his way.


\subsubsection*{Myranos} 
\sigil{Quincunx}
\words{Machen Sie Ihr eigenes Glück (Make your own luck).}
\colours{Yellow}
\alignment{Lawful Neutral}
Dwarven god of luck.  
  

\subsubsection*{Valeria} 
\sigil{Mountain Peak}
\words{Streik schnell für gerade Kanten (Strike fast for straight edges)}
\colours{Grey}
\alignment{Neutral}
Goddess of the arts and fertility  
  
\subsubsection*{Heratia} 
\sigil{Axe}
\words{Meine Leute zuerst}
\colours{White}
\alignment{Neutral}
Goddess of the hearth and home, protection and grudges.
Grudge against Orcs (oldest unclosed grudge)  

\subsubsection*{Chylos}
\sigil{Unicursal Valknut (three enwined triangles)}
\words{Brot, Bier und Kampf (Bread, Beer and Battle).}
\colours{Brown}
\alignment{Neutral}
God of the Afterlife  
  



\section*{The Old Gods}

\subsection*{The Gods in the East}

\subsubsection*{Tsathoggua}
\sigil{Toad}
\words{Totul pentru credincioșii (All for the faithfull)}
\colours{Turquoise}
\alignment{Evil}

The Toad-Demon, the whisperer in the darkness, the god Tsathoggua, abides from eldermost 
eons.  He is very squat and pot-bellied, his head is like that of a monstrous toad, his whole 
body is covered with short fur, giving a vague sensation of both the bat and the sloth. You 
shall know Tsathoggua by his great girth and his batlike 
furriness and the look of a sleepy black toad which he has eternally. He will rise not 
from his place, even in the ravening of hunger, but will wait in divine slothfulness for 
the sacrifice.   His sleepy lids are half-lowered over his globular eyes; and the tip of a 
forked tongue issues from his fat mouth.


\subsubsection*{Atlach-Nacha} 
\sigil{Spider}
\words{Pod de sânge (Bridge of Blood)}
\colours{Black}
\alignment{Lawful Evil}

The spider god.  Atlach-Nacha resembles a huge spider with an almost-human face. It dwells 
in the outer planes. There it spins a gigantic web, bridging the chasm of space between the 
outer planes and the waking world. Some believe that when the web is complete, the end of the 
world will come.
  

\subsubsection*{Quachil Uttaus}  
\sigil{Drop of Blood}
\words{Foamea de eoni (Hunger of the Eons)}
\colours{Light Grey}
\alignment{Evil}
  
Quachil Uttaus can reduce all living tissue that he comes into contact with to dust. Quachil 
Uttaus is usually associated with age, death, and decay. Summoning this god is lethal if one 
even subconsciously entertains thoughts of suicide.

Quachil Uttaus appears as a figure no larger than a young child, but sere and shriveled as 
some millennial mummy. Its hairless head, is unfeatured, borne on a neck of skeleton thinness, 
lined with a thousand reticulated wrinkles. The body is like that of some monstrous, withered 
abortion that had never drawn breath. The pipy arms, ending in bony claws, were outthrust as 
if ankylosed in a posture of an eternal dreadful groping.


\subsubsection*{Abhoth}
\sigil{Inverted Pentagram}
\words{Maestru de degradare (Master of Decay)}
\colours{Dark Grey}
\alignment{Chaotic Evil}
The Source of Uncleanliness.  Abhoth is a horrid, dark gray protean mass and is said to be 
the ultimate source of all miscreation and abomination.  Abhoth has a twisted and cynical 
mind, and communicates telepathically with others.
  

\subsubsection*{Orlim Shaikorth}
\sigil{Circular Mouth}
\words{Cel care mănâncă de toate lucrurile (The one who eats of all things)}
\colours{White}
\alignment{Neutral Evil}
The Eater, the white worm, the worm that gnaws in the night.  


\subsubsection*{Basatan}
\sigil{Crab Claw}
\words{Părtași de trupul meu (Partake of my flesh)}
\colours{Green}
\alignment{Chaotic Evil}
Master of the Crabs. A deity of the sea, who exerts power over 
the winds, the sea-currents, and the creatures of the deep.    Followers perform ritualistic canabalism.


\subsubsection*{Thamogorgos}
\sigil{Eye}
\words{Maestru de întuneric (Master of Darkness)}
\colours{Red}
\alignment{Lawful Evil}
Lord of the All.  King of all the demons, ruler of Hell.  He who waits in the darkness.
  
\end{document}
