\documentclass{letter}
\address{}
\begin{document}
\begin{letter}{}

\begin{tt}(written in aquillonian)\end{tt}
\date{}
\opening{To whom it may concern.}



                  They are within our walls.  The rookery has been taken so I can no longer send mesaage, though we hold the tower for now.  I prepare these notes so that the good works of the agents of Caiphon are not wasted.  If you find this information convey it to Uthan, commonly known as the Sagacious in Laibstadt and he will reward you for it.  Trust no others in this matter if you value your lives.  

Please look after Henri if he finds you and gives this information to you - he is a resourceful boy who works as diligently as one can expect from a boy his age.  He is an orphan.  Both his parents were killed by Drow raiders to the West.  Some refugees of the raid left him here as they were not in a position to care for him.

There are no other written records of the intrigue which is recorded here-in.  Such work had it been undertaken would have posed a great risk to those who gathered it.  I wonder, even now, whether I am being impetuous in committing it to paper.  Now that it is too late to communicate them in any other way I feel I must put my faith in the humble efforts of Henri, may Caiphon guide him, to get this information to those who need it most.  I record what we know here.

There are two factions of demon worshippers in Laibstadt, and indeed in Brythinnia, that we know of.  Those that call themselves the \emph{first}, the followers of Rlim Shaikorth, and those that style themselves the \emph{chosen}, followers of Abhoth and who others call \emph{the unclean}.

The two central tennets of the followers of the White Worm is the belief in the imminent arrival of Rlim Shaikorth which they call the \emph{Repast}, and a belief in Transubstantiation (when they are devoured they believe they will become one with their god).  They believe that if they serve in this life they shall be the first amongst the devoured on the day of Repast.  Their high priests have a strict order in which they believe they will be devoured.  The most high they call the \emph{Primus}, others are named accordingly, for example the late Hannus Vizeare was believed to be third amongst the First.  Second among the First is Grzegorz Thau, Duke of Gnampff and Thule ambassador to Brythynia in Laibstadt.  We have only heard rumours of the Primus.  He is known informally amongst his followers as the Butcher because he single-handedly slaughters so many offerings to their false god.

It is of utmost importance that you convey to Uthan that his manservant, Bruno, known as the incompetent has been seen in the presence of Lokhir Hightower, the Dark Elf Cultural Attache in Laibstadt.  Who knows what nefarious ends the Druchii seek but Uthan is in grave danger while in his presence.

Of the unclean ones we have heard but whispers in the wind.  It is clear that there has been some kind of struggle between the First and the Unclean however all the agents we have sent to infiltrate the first have disappeared.

In addition it appears that there seems to be a drop in the amount of coins in circulation in Laibstadt.   Large numbers of coins seem to have been removed from the economy or are being stockpiled somewhere.   We are not sure whether this is actually a cause for worry or just a reaction to some perceived instability in the markets.


\closing{Abbott Gaufridus FIRMIN \\
7/9/2203\\
May Caiphon's Cleansing Light Shine ever upon us all.}
\end{letter}
\end{document}
