\documentclass[a4paper]{dnd5}
\begin{document}

\section*{City Gates}

\begin{itemize}
\item Line of people waiting to get in to the city via the south gate, it's lunchtime.
\item LaibBerg, loaf mountain, can be seen in the distance.  Dwarvern silver mine.  There's 
      a series of rapids between there and here and Laibstadt is situated at the upper most navigable region of the Bruin River.
\item Putrid stench of decay eminates from the city.
\item City guards wearing the kings livery (a crown on mace and crossed sword) extorting 
      money from the people entering the gates. 
\item Caged bear in a wagon drawn by an ox, guards aren't going to let it through the gates
\item Adelbert Vizeare (minor Vizeare) is trying to get the bear into th gates, arguing with the guards. Who won't let him because it's dangerous.
\item People are throwing stones at it and stabbing it with sticks
\item Wheel is loose
\item Bear escapes. ``Stop that bear''.  
\item Simon the Borderlander and gang walking up the hill to the gates
\item Simon tries to get the reward by wrapping the rope tied around the bears neck to the cart.
\item If the players do nothing Simon fails and the bear charges them.
\item Adelbert gets angry if the party doesn't try to stop the bear.
\item Simon gets angry if they do (you owe me my bear catching money).
\end{itemize}

\begin{outs} 
\item The bear runs off
\item The guards distract the bear 
\end{outs}

\begin{purpose}
\item Set up conflict between borderlanders and the party
\item Introduces house Nerval and house Vizeare.
\item Paints a picture of a shades of grey world.
\item borderlander ambush
\end{purpose}
     
\end{document}

     

