\documentclass[a4paper]{dnd5}
\begin{document}

\section*{The Murenger Arms}

\begin{precis}
\item A pub, formerly the office of the Murenger
\item Proprietor is the fat dwarf Grundewald
\item He's been expecting them and is anxious to get them to help with his problem..
\item Grundewald: I must leave you I have business to attend to.
\item Uthan: We still have a little time left to us... introductions..
\item Uthan asks the omiscient one to go and check if the others have arrived.
\item Uthan asks "Tell me this: What would you do if they could see into the future?"
\item Gets Bruno to light the fire.. TOO doesn't like fire.. !important exposition.
TOO makes up for it in other ways of course.  His ability to glimpse the future is unsurpassed.
\item Uthan explains that he has spent his life trading knowledge.. But let's face it.. knowledge has almost know value.  It is only secrets that have any real value.
\item Needless to say that when he found TOO he was excited at the prospects for enriching himself.
\item Uthan explains the TOO can, and the future he has seen is apocalyptic.  
Time is like a leaf on a river.
The path can controlled somewhat.  
But we are heading for a disaster of cataclysmic proportions.
\item But for all his ability, and his ability is the greater by far than any others I have seen, it is not perfect.  Therefore there is hope.  
\item I had thought that I was a creatute of habit, set in my ways. So it comes as a surprise to me that in the ninty second year of my life, and having spent most of those years in the pursuit of gold, I should now find myself determined on a philanthropic venture.   
\item I am an old man and I suspect I may not have long to live.  
\item Yes, the thirst for self-enrichment within me has been suddenly and irreversibly quenched.
\item Instead, I have set myself a new goal.  One I pray to see through to its completion.  What goal you may ask?  No less than saving the world from it's imminent doom.
\item Furthermore, gentlemen, I have enlisted you as the vehicle by which I hope to achieve this objective, despite the extreme difficulty of the task.  Which explains the reason for our presence in this room.

\item It is the Summer Solstice today, said by some to be a good omen for a new venture.

\item Why us?
  Fate is a fickle creature.  It seems that you have both the glory and the misfortune to be chosen as its pawns.  In addition your backgrounds mean that I know that you have not yet been compromized.  Also by all reports you have some useful skills that we'd like to put to use.

\item TOO returns
\item Uthan: In any case we can wait no longer.. 
\item Uthan: The Others couldn't join us?  
TOO: No master I told you they would not be joining us.
Uthan: What about the unreliable one?  
TOO: He's being unreliable.  
\item This causes us some problems... players will have to handle both our problems at once.
yes master.. 
Uthan: but which one first?
\item Grundewald returns
\end{precis}


\begin{outs} 
\item If the characters try and get out of it offer them some money
\end{outs}

\begin{purpose}
\item Introduce uthan
\item Introduce the current problem 
\end{purpose}
     
\end{document}

