\documentclass[a4paper]{article}
\begin{document}

\section*{Sanguinem Maledicta}
Copied and Expurgated by August Bluome, from the writings of Mantas Adomėnas circa 200 years before the founding of the city.

To use magic is to exploit the potential difference of energies between this and other planes of existence.  At best it is an extremely dangerous field, some might say that it is the domain of heedless megalomaniacs and the suicidally curious.

However, Blood Magic is universally reviled as the most abhorrent of all forms of magic.  Its' practice is punishable by death in all the civilized kingdoms of the known world.  Which is to say Brythinia, the Hibernian Kingdoms, Cheruskia, Averoigne, Thule, Cormyr, Aquillonia, Samartia and so on.  But not, notably, Nagaroth, the lands of the Border Kingdoms, Stygia, Hyrkannia, Arkidia, and the Bandit Kingdoms. 

Life itself is a magical process.  It involves the flow of magic, that which imbues life, through a human corpus.  Blood magic is the heinous field of magic that draws from this source.


Requiring no innate ability to use, Blood Magic is often employed by amateurs and dabblers.  Fortunately this almost always results in the rapid and often horrific extermination of the practicer.  I feel compelled to state outright, lest the reader feel tempted by the promise of the great power that it offers, the things beyond are compelling in their lies and tantalizing in their promises.  The best future for one who strays even momentarily down this path is summary execution,  there is much more to be lost than merely one's life when dealing with Blood Magic.

Dearly as I would love to forget for all times that which I have learned.  It behooves all great practitioners of the arts to have some understanding of the theory of Blood Magic so as best to combat it when it is found.  Luckily, the theoretical foundations of the field are well known and easily grasped by those with a sound thaumaturgical background.  

The unit of measurement in all things in Blood Magic is the animus, a single human soul.  However, life may be drained from an individual in part through the use of various processes and procedures.  This is the the source of animation of all the undead creatures and all their motivation.

Blood Magic is incredibly powerful, and fortunately also extremely difficult to control.  For these reasons it is almost always used for brute force applications requiring large amounts of energy and little finesse.  The three most prevalent of these are communicating with the creatures that whisper in the night from beyond, cursing, and opening gates, entry points into this world from beyond.

To open a communication channel one sacrifices a small amount of animus in one of several procedures that I will not go into here, and repeatedly projects one of the many communicating spells through the small cosmic aperture created.  It is vitally important, if one is to retain one's sanity, that the proper precautions be taken.  There is no surer way to ensure one's own destruction than to open gates into the unknown, even one's small enough only for communication.  This is the approach that forms the basis of all scrying magics (and the reason why such magics are so rightly held in contempt).

To invoke a curse is a similar process.  Instead of opening a path for communication the caster opens a way for the agents of darkness to view this world from afar.  This allows them to effect this world.  Needless to say this is incredibly dangerous as those from beyond that watch us are grasping and insatiable, dreading the coldness of their own fell existence.  Curses are also easy to detect.  People can feel the unseen eye, the so called malocchio, upon them.  They are easy to disrupt using simple magic. Because of this the use of blood curses is seen as the domain of the weak and the desperate.

Thirdly, and finally, Blood Magic can be used to open gates to the other dimensions where things crawl in the darkness and scream from hunger.  To open a gate of any size requires so much power that it is extremely difficult (and dangerous) to open a gate of any reasonable size for any reasonable duration.

The formula for calculating the required energy to open a gate to another dimension is:

\[ Energy = k \pi r^2 (1 + d) \hspace{0.4em} animi/sec \]

Where $r$ is the radius of the gate in meters, $d$ is the depth of the gate .. a 
distance that depends on the type of gate inter-planar or intra-planar.  For intra-planar gates $d = 0$.  I shall keep $k$ unknown for reasons that should be obvious to the reader.  The student is urged to make the relevant calculations to compare this with other thaumaturgical sources of power.


For reasons unknown, contextual alignments seem to enhance the power of Blood Magic.  This is the reason that almost all blood magic rituals known to the author involve the careful placement of objects in alignment.   The most respected theoretical explanation for this is based on the so-called Resonance Propositions which argue that alignments occur when planes converge, that is, where the veil between two universes are at their weakest.  This theory explains the importance of astrological events, such as syzergy, occultation and even solstices to its' foul practitioners.  Some have suggested that ley lines, also represent such close alignments.  The only problem with these propositions is that no evidence has ever been found that supports the ley line proposition (and nor in this author's opinion will such evidence ever be found).

It is well known that Pure Light is abhorrent to the powers of Blood Magic.  There are many theories why this is so, but it is the author's opinion that they are mostly bunkum.

\end{document}
